Learning and Reputation under Monopoly and Duopoly: \\A Competing Bandits Approach

### 2018-08-28 paper/competing_bandits.tex
edits on related work

\subsection{Discussion and related work}

Adoption of better exploration algorithms is a form of ``innovation", the interplay between competition and innovation being a well-studied topic in economics, \eg \cite{barro2004economic,aghion2005competition}, dating back to \cite{schumpeter2010capitalism}. A familiar theme is an ``inverted-U relationship" between competition and innovation -- too little or too much competition is bad for innovation, but intermediate levels of competition tend to be better. While this literature focuses on R\&D costs of innovation, ``reputational costs" seem new and specific to exploration.

>>>>

\subsection{Discussion and related work} 
\swedit{We view the adoption of better exploration algorithms as a form of ``innovation", and thus our work is related to a longstanding economics literature on the interplay between competition and innovation,} \eg \cite{barro2004economic,aghion2005competition}, dating back to \cite{schumpeter2010capitalism}. A familiar theme is an ``inverted-U relationship" between competition and innovation -- too little or too much competition is bad for innovation, but intermediate levels of competition tend to be better. While this literature focuses on R\&D costs of innovation, ``reputational costs" seem new and specific to exploration.
